### 2017-04-06 writing/paper/sections/wilf.tex
Symmetry use in Wilf
- Refer to symmetry instead of doing the structural work.

Consider \(q_2 = \textpattern{}{1}{0/1,1/0,1/1}\). Avoiding this pattern
means that a permutation does not end with its maximum. We can perform a
similar
decomposition as before to get
\begin{equation*}
    \mathcal{\var}_2 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}}{}{}{\mathcal{C}\setminus\varepsilon}
\end{equation*}

% TODO Isn't q_3 a symmetry of q_2? So we don't need to repeat the work
Now consider \(q_3 = \textpattern{}{1}{0/0,0/1,1/0}\). The avoiders of this
pattern are permutations that do not start with their minimum. In this case we
perform the decomposition around the leftmost element
\begin{equation*}
    \mathcal{\var}_3 =\varepsilon \sqcup
\decompleft{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}
\end{equation*}
All of these classes have the same generating function, namely
\begin{equation}
    \var(x) = 1 + xC(x)(C(x)-1). \label{eqn:maxlgen}
\end{equation}
The coefficients of this generating function are
\begin{equation*}
    1, 0, 1, 3, 9, 28, 90, 297, 1001, 3432, 11934,\dotsc
\tag{\href{https://oeis.org/A000245}{OEIS: A000245} with offset \(1\)}
\end{equation*}

>>>>

Consider \(q_2 = \textpattern{}{1}{0/1,1/0,1/1}\). Avoiding this pattern
means that a permutation does not end with its maximum. We can perform a
similar
decomposition as before to get
\begin{equation*}
    \mathcal{\var}_2 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}}{}{}{\mathcal{C}\setminus\varepsilon}
\end{equation*}
The pattern \(q_3 = \textpattern{}{1}{0/0,0/1,1/0}\) is the reverse-complement-inverse
of \(q_2\) and hence the avoiders of \(q_2\) and \(q_3\) are equinumerous.
All of these classes have the same generating function, namely
\begin{equation}
    \var(x) = 1 + xC(x)(C(x)-1). \label{eqn:maxlgen}
\end{equation}
The coefficients of this generating function are
\begin{equation*}
    1, 0, 1, 3, 9, 28, 90, 297, 1001, 3432, 11934,\dotsc
\tag{\href{https://oeis.org/A000245}{OEIS: A000245} with offset \(1\)}
\end{equation*}
